The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-09 ms.tex
Fixing italics in one of the captions.

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\emph Top Panel:}Sources contributing
  to the heating rate of the CNM, $\vwO$, including stellar wind
  heating ({\it orange}), Ia supernovae ({\it green}), millisecond
  pulsars ({\it blue}), and compton heating (\it pink).  Each heating
  source varies with black hole mass $\Mbh$ due to the different
  average star formation history of galaxies of a given halo mass (see
  Appendix~\ref{app:windheat} for the detailed description). The total
  heating rate is shown in black. To account for the non-steady nature
  of the Ia heating we multiply the Ia heating by $e^{-\rs/\rIa}$, so
  the contribution that the heating contribiution from Ia supernovae
  will be suppressed if the time between successive supernovae is much
  greater than the dynamical time at $\rs$. {\emph Bottom panel} The
  ratio of the heating ($\dot{q}_{\rm heat}$) to the cooling rate
  ($\dot{q}_{\rm cool}$) at $\rs$ from the total heating rate in the
  top panel. Above $\Mbh\simeq 5\times 10^7 \Msun$ $\dot{q}_{\rm
    heat}(\rs)<\dot{q}_{\rm cool}(\rs)$ and a thermal instability
  would arise. The thermally unstable region is marked in red in the
  bottom panel. All curves become dashed in the thermally unstable
  region of parameter space: we expect our model to break down in this
  regime as the steady-state assumption would be violated.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\emph Top Panel:}Sources contributing
  to the heating rate of the CNM, $\vwO$, including stellar wind
  heating ({\it orange}), Ia supernovae ({\it green}), millisecond
  pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating
  source varies with black hole mass $\Mbh$ due to the different
  average star formation history of galaxies of a given halo mass (see
  Appendix~\ref{app:windheat} for the detailed description). The total
  heating rate is shown in black. To account for the non-steady nature
  of the Ia heating we multiply the Ia heating by $e^{-\rs/\rIa}$, so
  the contribution that the heating contribiution from Ia supernovae
  will be suppressed if the time between successive supernovae is much
  greater than the dynamical time at $\rs$. {\emph Bottom panel} The
  ratio of the heating ($\dot{q}_{\rm heat}$) to the cooling rate
  ($\dot{q}_{\rm cool}$) at $\rs$ from the total heating rate in the
  top panel. Above $\Mbh\simeq 5\times 10^7 \Msun$ $\dot{q}_{\rm
    heat}(\rs)<\dot{q}_{\rm cool}(\rs)$ and a thermal instability
  would arise. The thermally unstable region is marked in red in the
  bottom panel. All curves become dashed in the thermally unstable
  region of parameter space: we expect our model to break down in this
  regime as the steady-state assumption would be violated.}
\end{figure}
